APPM report - Draft

### 2022-10-25 paper_version/main.tex
Polish until the end. First version of the draft.

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{a4paper,scale=0.8}
\usepackage[square,numbers]{natbib}
\bibliographystyle{abbrvnat}
\usepackage{tikz}
\usepackage{tkz-euclide}
\usetikzlibrary{positioning, decorations.markings, arrows, intersections}
\usepackage{nicematrix}
\NiceMatrixOptions{cell-space-top-limit = 4pt}
\NiceMatrixOptions{cell-space-bottom-limit = 4pt}
\usepackage{tcolorbox}
\usepackage{caption, subcaption}
\usepackage{authblk}

@@

\newcommand{\todo}[1]{\textcolor{blue}{\fbox{\textbf{TODO: #1}}}}
\newcommand{\todobox}[1]{
    \begin{tcolorbox}[title=TODO list, colback=blue!10, colframe=blue]
        #1
    \end{tcolorbox}
}

@@

Each species in plasmas are treated as a compressible flow and assocated to one set of Euler equations that includes electromagnetic forces as well as other processes, e.g. collisions and recombination. The generic expressions are
\begin{align} \label{equ:euler_}
    \partial_t
    \begin{bmatrix}
    n_* \\
    m_*n_* \mathbf{u}_* \\
    m_*n_* e_*
    \end{bmatrix}
    + \nabla \cdot
    \begin{bmatrix}
    n_* \mathbf{u}_* \\
    m_*n_* \mathbf{u}_* \otimes \mathbf{u}_* + p_*\mathbb{I} \\
    m_*n_* h_* \mathbf{u}_*
    \end{bmatrix}
    =
    \begin{bmatrix}
    0 \\
    q_*n_*(\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
    \mathbf{J}_* \cdot \mathbf{E}
    \end{bmatrix}
    +
    \begin{bmatrix}
    \Gamma_* \\
    \mathbf{R}_* \\
    Q_*
    \end{bmatrix}.
\end{align}
The subscript $*$ represents the indices for different species, and by convention we assign $* = e$ to electrons, $* = i$ to ions, and $* = n$ to neutral atoms. The involved fluid quantities are: number density $n_*$, particle mass $m_*$,  charge number $q_*$, velocity $\mathbf{u}_*$, pressure $p_*$, specific total energy $e_* := \frac{1}{2}|\mathbf{u}_*|^2 + \frac{p_*}{m_*n_*(\gamma - 1)}$, specific total enthalpy $h_* := e_* + \frac{p_*}{m_*n_*}$ and current density $\mathbf{J}_* := q_*n_*\mathbf{u}_*$. All the species are assumed ideal gases with heat capacity ratio $\gamma=5/3$ for monatomic gases. The left-hand side of the equations describes the convection of plasma fluids. The first term at the right-hand side denotes Lorentz force in the momentum equation and Joule heating in the energy equation. $\Gamma_*, \mathbf{R}_*, Q_*$ are generic terms due to effects of inter-species collision, ionization, recombination, etc.

@@

By abuse of notation, the dimensionless quantities have the same symbol with their original ones without incurring any ambiguity. For the sake of simplicity, we only consider the collision terms, namely $\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = Q_*^\text{coll}$ in (\ref{equ:euler_}), while neglecting other effects. The rescaled Euler-Maxwell system reads
\begin{subequations}
\begin{align}
    \beta \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescalling} \\ 
    \lambda^2 \partial_t \mathbf{D} - \frac{\beta \lambda^2}{\xi^2}\nabla \times \mathbf{H} &= - \frac{\zeta}{\eta M^2}\mathbf{J}, \label{equ:maxwell_ampere_rescalling} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescalling}\\
    \lambda^2 \eta M^2 \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D_rescalling} \\
    \partial_t
    \begin{bmatrix}
    n_* \\
    n_* \mathbf{u}_* \\
    n_* e_*
    \end{bmatrix}
    + \nabla \cdot
    \begin{bmatrix}
    \zeta n_* \mathbf{u}_* \\
    \zeta n_* \mathbf{u}_* \otimes \mathbf{u}_* + \zeta M^{-2} \varepsilon_*^{-2} p_*\mathbb{I} \\
    \zeta n_* h_* \mathbf{u}_*
    \end{bmatrix}
    &=
    \begin{bmatrix}
    0 \\
    \eta \zeta \varepsilon_*^{-2} q_* n_*\mathbf{E} + \eta \zeta^2 \beta \varepsilon_*^{-2} q_* n_* \mathbf{u}_* \times \mathbf{B} \\
    \zeta \eta \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
    \end{bmatrix} +
    \begin{bmatrix}
    0 \\
    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
    \varepsilon_*^{-2}Q_*^{\text{coll}} \\
    \end{bmatrix}, \label{equ:euler_rescalling}
\end{align}
\end{subequations}
where the equation of state becomes $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + M^{-2}\frac{p_*}{\epsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + M^{-2}\frac{p_*}{\epsilon^2_* n_*}$. For a fully-ionized gas, we have the original expression of $\mathbf{R}_*^{\text{coll}}$ in (\ref{equ:collision}), and its rescaled expression becomes
\begin{equation*}
    \mathbf{R}_i^{\text{coll}} = \frac{Z\text{ln}\Lambda}{16\pi}g\lambda^{-1}M^{-1}\varepsilon_en_en_i(\mathbf{u}_i - \mathbf{u}_e). 
\end{equation*}

@@

Under such assumptions on these dimensionless parameters, the rescaled Euler-Maxwell system is simplified into a parametric system with the dimensionless Debye length $\lambda$ being the asymptotic parameter
\begin{subequations}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescaled} \\ 
    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= - \mathbf{J}, \label{equ:maxwell_ampere_rescaled} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescaled}\\
    \lambda^2 \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D_rescaled} \\
    \partial_t
    \begin{bmatrix}
    n_* \\
    n_* \mathbf{u}_* \\
    n_* e_*
    \end{bmatrix}
    + \nabla \cdot
    \begin{bmatrix}
    n_* \mathbf{u}_* \\
    n_* \mathbf{u}_* \otimes \mathbf{u}_* + \varepsilon_*^{-2} p_*\mathbb{I} \\
    n_* h_* \mathbf{u}_*
    \end{bmatrix}
    &=
    \begin{bmatrix}
    0 \\
    \varepsilon_*^{-2} q_* n_* (\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
    \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
    \end{bmatrix}+
    \begin{bmatrix}
    0 \\
    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
    \varepsilon_*^{-2}Q_*^{\text{coll}} 
    \end{bmatrix}, \label{equ:euler_rescaled}
\end{align}
\end{subequations}
with the equation of state $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + \frac{p_*}{\varepsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + \frac{p_*}{\varepsilon^2_* n_*}$. For a fully-ionized gas with only ions and electrons, 
\begin{equation} \label{equ:collision_rescaled} 
    \mathbf{R}_i^{\text{coll}} = \alpha^{\text{coll}}n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_e^{\text{coll}},
\end{equation}
and consequently, the rescaled friction heat for ions and electrons takes the expression
\begin{align*} 
    Q_i^{\text{coll}} &= \alpha^{\text{coll}}n_en_i \mathbf{u}_i (\mathbf{u}_i - \mathbf{u}_e), \\
    Q_e^{\text{coll}} &= \alpha^{\text{coll}}n_en_i \mathbf{u}_e (\mathbf{u}_e - \mathbf{u}_i).
\end{align*}

@@

We consider a simply connected domain $\Omega$ that is decomposed into two sub-domains $\Omega_P$ and $\Omega_I$ representing plasma domain and insulating domain respectively. We use the notation $\Gamma_C := \partial\Omega \cap \partial\Omega_P$, denoting the contact boundary, and $\Gamma_I := \partial\Omega \cap \partial\Omega_I$ for the insulating boundary which an artificial cut-off boundary. The interface between the two domains is denoted by $\Gamma_W = \partial\Gamma_I \cap \partial\Gamma_P$. A geometric arrangement corresponding to his setting is visualized in Fig. \ref{fig:domain_sketch}.

@@

The Maxwell system is defined on the whole domain $\Omega$. External voltages are enforced on the contact boundary $\Gamma_C$ to model electrodes. More specifically, $\Gamma_C$ is composed of two disjoint connecting components $\Gamma_C^\pm$. Constant potentials are enforced on each component in the sense that $\Phi|_{\Gamma_C^\pm} = \Phi_\pm$. The insulating boundary blocks the energy interchange and therefore only admits zero electric and magnetic flux, in the sense that $\text{curl}\mathbf{E}\cdot \mathbf{n} = 0$ and $\text{curl}\mathbf{H}\cdot \mathbf{n} = 0$ where $\mathbf{n}$ is the outer normal vector. \todo{A few works on ECE BC?} 
\begin{figure}
\begin{minipage}{0.45\textwidth}
    \resizebox{\textwidth}{!}{
    \begin{tikzpicture}
    \coordinate (O1) at (0,0);
    \draw[violet] (O1) circle (1) node[blue] {Electrode};
    \fill[blue, opacity=0.2] (O1) circle (1);
    \draw[very thick] (O1) circle (1.5);
    \coordinate (O2) at (4.5,1);
    \draw[violet] (O2) circle (1);
    \node at (O2) {\textcolor{red}{Electrode}};
    \node at (barycentric cs:O1=1,O2=1) {Plasma}; 
    \fill[red, opacity=0.2] (O2) circle (1);
    \coordinate (S1) at ([shift={(-0.196,0.98)}]O1);
    \coordinate (S2) at ([shift={(-0.196,0.98)}]O2);
    \coordinate (P1) at ([shift={(0.196,-0.98)}]O1);
    \coordinate (P2) at ([shift={(0.196,-0.98)}]O2);
    \draw[violet] (S1) -- (S2);
    \draw[violet] (P1) -- (P2);
    \coordinate (SS1) at ([shift={({-0.196*1.5},{0.98*1.5})}]O1);
    \coordinate (SS2) at ([shift={({-0.196*1.5},{0.98*1.5})}]O2);
    \coordinate (PP1) at ([shift={({0.196*1.5},{-0.98*1.5})}]O1);
    \coordinate (PP2) at ([shift={({0.196*1.5},{-0.98*1.5})}]O2);
    \draw[very thick] (SS1) -- (SS2);
    \draw[very thick] (PP1) -- (PP2); 
    \draw[black, very thick] (SS2) arc (101.31:180+101.31:1.5);
    \draw[very thick] (PP2) arc (101.31-180:101.31:1.5);
    \draw[-to] (barycentric cs:SS1=1,SS2=1,S1=1,S2=1) to[out=90,in=0] ([shift={(-0.5,0.5)}]barycentric cs:SS1=1,SS2=1,S1=1,S2=1) node[left, gray] {Insulator};
    \begin{scope}[shift={(5.5,-1.4)}]
    \draw[blue, -to] (0,0) -- (0.65,0.12) node[right]{\small $z$};
    \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
    \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
    \end{scope}
    \end{tikzpicture}}
\end{minipage}
\begin{minipage}{0.49\textwidth}
    \resizebox{1.1\textwidth}{!}{ \begin{tikzpicture}
        \coordinate (A1) at (0,1.5);
        \coordinate (A2) at (0,1);
        \coordinate (A3) at (0,-1);
        \coordinate (A4) at (0,-1.5);
        \coordinate (B1) at (6,1.5);
        \coordinate (B2) at (6,1);
        \coordinate (B3) at (6,-1);
        \coordinate (B4) at (6,-1.5);
        \draw[violet] (A2) -- node[above]{\color{gray}Insulating domain $\Omega_I$} node[black, below]{\textcolor{violet}{$\Gamma_W$}} (B2);
        \draw[violet] (A3) -- node[below]{\color{gray}Insulating domain $\Omega_I$} node[black, above]{\textcolor{violet}{$\Gamma_W$}} (B3);
        \draw[very thick] (A2) -- (A1) -- node[above]{$\Gamma_I$}  (B1) -- (B2);
        \draw[very thick] (A3) -- (A4) -- node[below]{$\Gamma_I$} (B4) -- (B3);
        \draw[very thick, dashed, blue] (A2) -- node[left] {$\Gamma_C^1$} (A3);
        \draw[very thick, dashed, red]  (B2) -- node[right] {$\Gamma_C^2$}  (B3);
        \node at (3,0) {Plasma domain $\Omega_P$};
        \begin{scope}[shift={(6.5,-1.6)}]
        \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
        \draw[blue, -to] (0,0) -- (0.7,0) node[right]{\small $z$};
        \end{scope}
    \end{tikzpicture}}
\end{minipage}
\caption{Sketch of the domain. The right figure shows the cross section on the $x$-$z$ plane.}
\label{fig:domain_sketch}
\end{figure}

@@

\vspace{10pt}
\begin{minipage}[t]{0.49\textwidth}
    \textbf{For the Euler equations:}
    \begin{align*}
    \mathbf{u_*}\cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W, \\
    \text{grad}n_* \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W. \\
    \text{grad}e_* \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W. \\
    \text{grad}\mathbf{U_*} \cdot \mathbf{n} &= \mathbf{0} \ \ \text{on} \ \ \Gamma_C.
\end{align*}
\end{minipage}
\begin{minipage}[t]{0.49\textwidth}
    \textbf{For Maxwell's equations:}
    \begin{align*}
    \Phi = \Phi^\pm(t)\ \ &\text{on} \ \ \Gamma_C^\pm, \\
    \text{curl} \mathbf{E} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \Gamma_I,  \\
    \text{curl} \mathbf{H} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \Gamma_I.\
    \end{align*}
\end{minipage}

@@

\subsection{Reformulation} \label{sec:reform_continuous}
In the insulating domain $\Omega_I$ (see Fig. \ref{fig:sketch_domain}), the Euler system is not defined there due to the absence of plasmas. Consequently, the Maxwell system in $\Omega_I$ is described by
\begin{subequations}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:faraday_ins}\\ 
    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= 0,  \label{equ:ampere_ins}\\
    \nabla \cdot \mathbf{B} &= 0, \label{equ:gauss_B_ins}\\
    \lambda^2 \nabla \cdot \mathbf{D} &= 0 \label{equ:gauss_D_ins}.
\end{align}
\end{subequations}

In non-neutral regime where $\lambda = \mathcal{O}(1)$, the Maxwell system in $\Omega_I$ is well-posed and Gauss's laws (\ref{equ:gauss_B_ins}) (\ref{equ:gauss_D_ins}) are redundant as long as they are satisfied at initial moment. Nonetheless, as the system approaches the quasi-neutral limit as $\lambda \rightarrow 0$, Gauss's law for $\mathbf{D}$-field (\ref{equ:gauss_D_ins}) becomes degenerate. Due to limited precision of computers, schemes based on this set of PDEs would run into instability. The vanishing divergence would be broken down as $\nabla \cdot \mathbf{D} = 0/\lambda^2 = 0$ would not hold numerically when $\lambda^2$ becomes extremely small.

To see this issue from another perspective, we observe the limit Maxwell system in $\Omega_I$
\begin{subequations}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:faraday_ins_limit}\\ 
    - \nabla \times \mathbf{H} &= 0,  \label{equ:ampere_ins_limit}\\
    \nabla \cdot \mathbf{B} &= 0, \label{equ:gauss_B_ins_limit}\\
    \nabla \cdot \mathbf{D} &= 0 \label{equ:gaus_D_ins_limit}.
\end{align}
\end{subequations}

@@

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{a4paper,scale=0.8}
\usepackage[square,numbers]{natbib}
\bibliographystyle{abbrvnat}
\usepackage{tikz}
\usepackage{tkz-euclide}
\usetikzlibrary{positioning, decorations.markings, arrows, intersections}
\usepackage{nicematrix}
\NiceMatrixOptions{cell-space-top-limit = 4pt}
\NiceMatrixOptions{cell-space-bottom-limit = 4pt}
\usepackage{tcolorbox}
\usepackage{caption, subcaption}
\usepackage{authblk}
\usepackage{soul}

@@

\newcommand{\mycolorbox}[2]{\colorbox{#1}{$\displaystyle#2$}}
\newcommand{\todo}[1]{\textcolor{blue}{\fbox{\textbf{TODO: #1}}}}
\newcommand{\todobox}[1]{
    \begin{tcolorbox}[title=TODO list, colback=blue!10, colframe=blue]
        #1
    \end{tcolorbox}
}

@@

Each species in plasmas are treated as a compressible flow and assocated to one set of Euler equations that includes electromagnetic forces as well as other processes, e.g. collisions and recombination. The generic expressions are
\begin{align} \label{equ:euler_}
    \partial_t
    \begin{pmatrix}
    n_* \\
    m_*n_* \mathbf{u}_* \\
    m_*n_* e_*
    \end{pmatrix}
    + \nabla \cdot
    \begin{pmatrix}
    n_* \mathbf{u}_* \\
    m_*n_* \mathbf{u}_* \otimes \mathbf{u}_* + p_*\mathbb{I} \\
    m_*n_* h_* \mathbf{u}_*
    \end{pmatrix}
    =
    \begin{pmatrix}
    0 \\
    q_*n_*(\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
    \mathbf{J}_* \cdot \mathbf{E}
    \end{pmatrix}
    +
    \begin{pmatrix}
    \Gamma_* \\
    \mathbf{R}_* \\
    Q_*
    \end{pmatrix}.
\end{align}
The subscript $*$ represents the indices for different species, and by convention we assign $* = e$ to electrons, $* = i$ to ions, and $* = n$ to neutral atoms. The involved fluid quantities are: number density $n_*$, particle mass $m_*$,  charge number $q_*$, velocity $\mathbf{u}_*$, pressure $p_*$, specific total energy $e_* := \frac{1}{2}|\mathbf{u}_*|^2 + \frac{p_*}{m_*n_*(\gamma - 1)}$, specific total enthalpy $h_* := e_* + \frac{p_*}{m_*n_*}$ and current density $\mathbf{J}_* := q_*n_*\mathbf{u}_*$. All the species are assumed ideal gases with heat capacity ratio $\gamma=5/3$ for monatomic gases. The left-hand side of the equations describes the convection of plasma fluids. The first term at the right-hand side denotes Lorentz force in the momentum equation and Joule heating in the energy equation. $\Gamma_*, \mathbf{R}_*, Q_*$ are generic terms due to effects of inter-species collision, ionization, recombination, etc.

@@

By abuse of notation, the dimensionless quantities have the same symbol with their original ones without incurring any ambiguity. For the sake of simplicity, we only consider the collision terms, namely $\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = Q_*^\text{coll}$ in (\ref{equ:euler_}), while neglecting other effects. The rescaled Euler-Maxwell system reads
\begin{subequations}
\begin{align}
    \beta \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescalling} \\ 
    \lambda^2 \partial_t \mathbf{D} - \frac{\beta \lambda^2}{\xi^2}\nabla \times \mathbf{H} &= - \frac{\zeta}{\eta M^2}\mathbf{J}, \label{equ:maxwell_ampere_rescalling} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescalling}\\
    \lambda^2 \eta M^2 \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D_rescalling} \\
    \partial_t
    \begin{pmatrix}
    n_* \\
    n_* \mathbf{u}_* \\
    n_* e_*
    \end{pmatrix}
    + \nabla \cdot
    \begin{pmatrix}
    \zeta n_* \mathbf{u}_* \\
    \zeta n_* \mathbf{u}_* \otimes \mathbf{u}_* + \zeta M^{-2} \varepsilon_*^{-2} p_*\mathbb{I} \\
    \zeta n_* h_* \mathbf{u}_*
    \end{pmatrix}
    &=
    \begin{pmatrix}
    0 \\
    \eta \zeta \varepsilon_*^{-2} q_* n_*\mathbf{E} + \eta \zeta^2 \beta \varepsilon_*^{-2} q_* n_* \mathbf{u}_* \times \mathbf{B} \\
    \zeta \eta \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
    \end{pmatrix} +
    \begin{pmatrix}
    0 \\
    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
    \varepsilon_*^{-2}Q_*^{\text{coll}} \\
    \end{pmatrix}, \label{equ:euler_rescalling}
\end{align}
\end{subequations}
where the equation of state becomes $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + M^{-2}\frac{p_*}{\epsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + M^{-2}\frac{p_*}{\epsilon^2_* n_*}$. For a fully-ionized gas, we have the original expression of $\mathbf{R}_*^{\text{coll}}$ in (\ref{equ:collision}), and its rescaled expression becomes
\begin{equation*}
    \mathbf{R}_i^{\text{coll}} = \frac{Z\text{ln}\Lambda}{16\pi}g\lambda^{-1}M^{-1}\varepsilon_en_en_i(\mathbf{u}_i - \mathbf{u}_e). 
\end{equation*}

@@

Under such assumptions on these dimensionless parameters, the rescaled Euler-Maxwell system is simplified into a parametric system with the dimensionless Debye length $\lambda$ being the asymptotic parameter
\begin{subequations}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescaled} \\ 
    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= - \mathbf{J}, \label{equ:maxwell_ampere_rescaled} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescaled}\\
    \lambda^2 \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D_rescaled} \\
    \partial_t
    \begin{pmatrix}
    n_* \\
    n_* \mathbf{u}_* \\
    n_* e_*
    \end{pmatrix}
    + \nabla \cdot
    \begin{pmatrix}
    n_* \mathbf{u}_* \\
    n_* \mathbf{u}_* \otimes \mathbf{u}_* + \varepsilon_*^{-2} p_*\mathbb{I} \\
    n_* h_* \mathbf{u}_*
    \end{pmatrix}
    &=
    \begin{pmatrix}
    0 \\
    \varepsilon_*^{-2} q_* n_* (\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
    \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
    \end{pmatrix}+
    \begin{pmatrix}
    0 \\
    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
    \varepsilon_*^{-2}Q_*^{\text{coll}} 
    \end{pmatrix}, \label{equ:euler_rescaled}
\end{align}
\end{subequations}
with the equation of state $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + \frac{p_*}{\varepsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + \frac{p_*}{\varepsilon^2_* n_*}$. For a fully-ionized gas with only ions and electrons, 
\begin{equation} \label{equ:collision_rescaled} 
    \mathbf{R}_i^{\text{coll}} = \alpha^{\text{coll}}n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_e^{\text{coll}},
\end{equation}
and consequently, the rescaled friction heat for ions and electrons takes the expression
\begin{align*} 
    Q_i^{\text{coll}} &= \alpha^{\text{coll}}n_en_i \mathbf{u}_i (\mathbf{u}_i - \mathbf{u}_e), \\
    Q_e^{\text{coll}} &= \alpha^{\text{coll}}n_en_i \mathbf{u}_e (\mathbf{u}_e - \mathbf{u}_i).
\end{align*}

@@

We consider a simply connected domain $\Omega$ that is decomposed into two sub-domains $\Omega_P$ and $\Omega_N$ representing plasma domain and non-conducting domain respectively. We use the notation $\Gamma_C := \partial\Omega \cap \partial\Omega_P$, denoting the contact boundary, and $\Gamma_I := \partial\Omega \cap \partial\Omega_N$ for the insulating boundary which an artificial cut-off boundary. The interface between the two domains is denoted by $\Gamma_W = \partial\Omega_I \cap \partial\Omega_P$. A geometric arrangement corresponding to this setting is visualized in Fig. \ref{fig:domain_sketch} and is the one used in \cite[][ch. 1, sec. 4]{fuchs_2021}.

@@

The Maxwell system is defined on the whole domain $\Omega$. External voltages are enforced on the contact boundary $\Gamma_C$ to model electrodes. More specifically, $\Gamma_C$ is composed of two disjoint connecting components $\Gamma_C^\pm$. Constant potentials are enforced on each component in the sense that $\Phi|_{\Gamma_C^\pm} = \Phi_\pm$. The insulating boundary blocks the energy interchange and therefore only admits zero electric and magnetic flux, in the sense that $\text{curl}\mathbf{E}\cdot \mathbf{n} = 0$ and $\text{curl}\mathbf{H}\cdot \mathbf{n} = 0$ where $\mathbf{n}$ is the outer normal vector. \todo{ECE BC} 
\begin{figure}
\begin{minipage}{0.45\textwidth}
    \resizebox{\textwidth}{!}{
    \begin{tikzpicture}
    \coordinate (O1) at (0,0);
    \draw[violet] (O1) circle (1) node[blue] {Electrode};
    \fill[blue, opacity=0.2] (O1) circle (1);
    \draw[very thick] (O1) circle (1.5);
    \coordinate (O2) at (4.5,1);
    \draw[violet] (O2) circle (1);
    \node at (O2) {\textcolor{red}{Electrode}};
    \node at (barycentric cs:O1=1,O2=1) {Plasma}; 
    \fill[red, opacity=0.2] (O2) circle (1);
    \coordinate (S1) at ([shift={(-0.196,0.98)}]O1);
    \coordinate (S2) at ([shift={(-0.196,0.98)}]O2);
    \coordinate (P1) at ([shift={(0.196,-0.98)}]O1);
    \coordinate (P2) at ([shift={(0.196,-0.98)}]O2);
    \draw[violet] (S1) -- (S2);
    \draw[violet] (P1) -- (P2);
    \coordinate (SS1) at ([shift={({-0.196*1.5},{0.98*1.5})}]O1);
    \coordinate (SS2) at ([shift={({-0.196*1.5},{0.98*1.5})}]O2);
    \coordinate (PP1) at ([shift={({0.196*1.5},{-0.98*1.5})}]O1);
    \coordinate (PP2) at ([shift={({0.196*1.5},{-0.98*1.5})}]O2);
    \draw[very thick] (SS1) -- (SS2);
    \draw[very thick] (PP1) -- (PP2); 
    \draw[black, very thick] (SS2) arc (101.31:180+101.31:1.5);
    \draw[very thick] (PP2) arc (101.31-180:101.31:1.5);
    \draw[-to] (barycentric cs:SS1=1,SS2=1,S1=1,S2=1) to[out=90,in=0] ([shift={(-0.5,0.5)}]barycentric cs:SS1=1,SS2=1,S1=1,S2=1) node[left, gray] {Insulator};
    \begin{scope}[shift={(5.5,-1.4)}]
    \draw[blue, -to] (0,0) -- (0.65,0.12) node[right]{\small $z$};
    \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
    \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
    \end{scope}
    \end{tikzpicture}}
\end{minipage}
\begin{minipage}{0.49\textwidth}
    \resizebox{1.1\textwidth}{!}{ \begin{tikzpicture}
        \coordinate (A1) at (0,1.5);
        \coordinate (A2) at (0,1);
        \coordinate (A3) at (0,-1);
        \coordinate (A4) at (0,-1.5);
        \coordinate (B1) at (6,1.5);
        \coordinate (B2) at (6,1);
        \coordinate (B3) at (6,-1);
        \coordinate (B4) at (6,-1.5);
        \draw[violet] (A2) -- node[above]{\color{gray}Non-conducting domain $\Omega_N$} node[black, below]{\textcolor{violet}{$\Gamma_W$}} (B2);
        \draw[violet] (A3) -- node[below]{\color{gray}Non-conducting domain $\Omega_N$} node[black, above]{\textcolor{violet}{$\Gamma_W$}} (B3);
        \draw[very thick] (A2) -- (A1) -- node[above]{$\Gamma_I$}  (B1) -- (B2);
        \draw[very thick] (A3) -- (A4) -- node[below]{$\Gamma_I$} (B4) -- (B3);
        \draw[very thick, dashed, blue] (A2) -- node[left] {$\Gamma_C^1$} (A3);
        \draw[very thick, dashed, red]  (B2) -- node[right] {$\Gamma_C^2$}  (B3);
        \node at (3,0) {Plasma domain $\Omega_P$};
        \begin{scope}[shift={(6.5,-1.6)}]
        \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
        \draw[blue, -to] (0,0) -- (0.7,0) node[right]{\small $z$};
        \end{scope}
    \end{tikzpicture}}
\end{minipage}
\caption{Sketch of the domain. The right figure shows the cross section on the $x$-$z$ plane.}
\label{fig:domain_sketch}
\end{figure}

@@

\vspace{10pt}
\begin{minipage}[t]{0.49\textwidth}
    \textbf{For the Euler equations:}
    \begin{align*}
    \mathbf{u_*}\cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W, \\
    \text{grad}n_* \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W. \\
    \text{grad}e_* \cdot \mathbf{n} &= 0 \ \ \text{on} \ \ \Gamma_W. \\
    \text{grad}\mathbf{U_*} \cdot \mathbf{n} &= \mathbf{0} \ \ \text{on} \ \ \Gamma_C.
\end{align*}
\end{minipage}
\begin{minipage}[t]{0.49\textwidth}
    \textbf{For Maxwell's equations:}
    \begin{align*}
    \Phi = \Phi(t)\ \ &\text{on} \ \ \Gamma_C, \\
    \text{curl} \mathbf{E} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \Gamma_I,  \\
    \text{curl} \mathbf{H} \cdot \mathbf{n} = 0\ \ &\text{on} \ \  \Gamma_I.\
    \end{align*}
\end{minipage}

@@

\subsection{Reformulation} \label{sec:reform_continuous}
In the non-conducting domain $\Omega_N$ (see Fig. \ref{fig:domain_sketch}), the Euler system is not defined there due to the absence of plasmas. Consequently, the Maxwell system in $\Omega_N$ is described by
\begin{subequations}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:faraday_ins}\\ 
    \lambda^2 \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= 0,  \label{equ:ampere_ins}\\
    \nabla \cdot \mathbf{B} &= 0, \label{equ:gauss_B_ins}\\
    \lambda^2 \nabla \cdot \mathbf{D} &= 0 \label{equ:gauss_D_ins}.
\end{align}
\end{subequations}

In non-neutral regime where $\lambda = \mathcal{O}(1)$, the Maxwell system in $\Omega_N$ is well-posed and Gauss's laws (\ref{equ:gauss_B_ins}) (\ref{equ:gauss_D_ins}) are redundant as long as they are satisfied at initial moment. Nonetheless, as the system approaches the quasi-neutral limit as $\lambda \rightarrow 0$, Gauss's law for $\mathbf{D}$-field (\ref{equ:gauss_D_ins}) becomes degenerate. Due to limited precision of computers, schemes based on this set of PDEs would run into instability. The vanishing divergence would be broken down as $\nabla \cdot \mathbf{D} = 0/\lambda^2 = 0$ would not hold numerically when $\lambda^2$ becomes extremely small.

To see this issue from another perspective, we observe the limit Maxwell system in $\Omega_N$
\begin{subequations}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:faraday_ins_limit}\\ 
    - \nabla \times \mathbf{H} &= 0,  \label{equ:ampere_ins_limit}\\
    \nabla \cdot \mathbf{B} &= 0, \label{equ:gauss_B_ins_limit}\\
    \nabla \cdot \mathbf{D} &= 0 \label{equ:gaus_D_ins_limit}.
\end{align}
\end{subequations}

@@

\begin{remark}
    In the implementation, it always provides convenience to index a pair of corresponding primal and dual elements with the same number. For instance, a primal face $A_k$ is penetrated by the dual edge $\Tilde{L}_k$. In the following discussion, we stick to this convention, which would simplify our notation.
\end{remark}
